\cvsection{Experience}
\begin{cventries}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
  \cventry
    {AI Developer}
    {Densyfy Inc.}
    {London, ON}
    {August 2017 - Current}
    {
	\begin{itemize}
		\item
		Building a machine learning infrastructure for densified video processing based on computer vision, speech, audio, cyber physical systems, etc.
		\item
		Leading a team for developing an inhouse data center for creating specific dataset for specific purpose.
		\item
		Design and develop different machine learning systems, insights, and algorithms, and then prototype, deploy to production, and test them to ensure all client’s business needs are covered.
		\item
		Developing a framework for validating the solution and manage overall software implementation lifecycles of projects, ensuring compliance with existing and future enterprise implementation standards.
		\item
		Optimizing algorithms and prototyping solutions for efficient implementation. Extending prototypes into fully functional, polished solutions ready for internal and/or external use. Supporting projects with thorough documentation of usage, design decisions and capabilities.
		\item
		Integration of voice recognition system for speaker diarization. Extensively worked with latest soa deep speech learning platform like DeepSpeech.		
	\end{itemize}
    }

  \cventry
  {Researcher, RoadLab}
  {Western University}
  {London, ON}
  {August 2013 - Current}
  {
  	\begin{itemize}
		\item
		Working as a researcher in RoadLab which aims to understand the driver's intent for the automated vehicle framework.(Linux, C++)
		\item
		Developed softwares for maneuver prediction based on driver's intent. The data acquired from an instrumented vehicle loaded with on board diagnostic tools and stereo cameras.
		\item
		Exhaustively applied deep learning frameworks for on road significant object detection.
		\item
		Developing a framework for on road traffic event recognition and integrate it with iADAS prediction framework.
		\item
		Optimizing algorithms and prototyping solutions for efficient implementation.	
	\end{itemize}
  }

  \cventry
    {Researcher, DIRC Lab}
    {Kingston University and LG Electronics (Korea). }
    {London, UK}
    {January 2010 – April 2010}
    {
    \begin{itemize}
    	\item
		Embedded software development for cell phones, testing and performance evaluation of surveillance video analysis using C++ and web application using Java script.
		\item
		Designed experiments in the cluster for better processing in Linux OS using Eclipse.
		\item
		Developed an algorithm to evaluate the performance of the combination of local features of tracking objects for LG Electronics, Korea (Eclipse, Java, SVM).
		\item
		Designed and developed tools for detection and tracking articulate human motion in unconstrained scenarios using a single surveillance camera (C++, Boost, MATLAB, SVM).
		\item
		Designed and developed tools to track silhouettes in videos to solve nonlinear articulated pedestrian tracking problem (C++, Boost, MATLAB, SVM).		
	\end{itemize}
    }

  \cventry
  {Assistant Manager (I.T.)}
  {Multimode Group, Microsoft Division }
  {Dhaka, Bangladesh}
  {January 2004 - January 2007}
  {
	\begin{itemize}
		\item
		Worked as an Assistant System Manager, responsible for providing software solutions for more than 500 employees. It was a team of 8 people providing embedded technical solutions inside the group of companies.
		\item
		I was responsible to provide technical solutions using Microsoft products. For the software development I had implemented the ERP software in C++ and SQL Server. I have planned, designed the information system of the company and implemented. I was involved in upgrading the software by adding new features and maintained it for two years in a resource constrained environment.
		\item
		Actively participated in UI design, feature development and conceptualization.
		\item
		I was in charge of the communication with the clients, arranged workshops to share views.
		\item
		Involved in web based software quality testing and responsible for making marketing policies, improving the business areas for Microsoft products.
		\item
		Have experience in working with full project life cycle, specially designing, developing and support phase.		
	\end{itemize}
  }
\end{cventries}
