\cvsection{Relevant Skills}
\begin{itemize}
\tightlist
\item
  More than 5 years of experience in programming language and algorithm design.
\item
  Worked as a researcher of a team for software development and performance evaluation.
\item  
  Designed experiments in the cluster for better processing.
\item  
  Successfully maintained flow of product supply chain management locally. 
\item  
  Involved in web based software quality testing and responsible for making marketing policies, improving the business areas for Microsoft products. 
\end{itemize}

\cvsection{Professional Specialization}
\begin{itemize}
\tightlist
\item
  Artificial Intelligence
\item  
  Computer Vision
\item  
  Machine Learning, Deep Learning and Big Data Analysis
\item  
  Pattern Recognition.
\item  
  Image Processing and Analysis 
\item  
  Robotic Vision
\item  
  Intelligent System Software Development 
\end{itemize}

\cvsection{Personal Projects}

\begin{itemize}
\tightlist
\item
  Basic Darknet detector for the Canadian Traffic Light Dataset.
\item
  RCNN framework for recognizing baseball actions in videos
\item
  A Keras implementation of acoustic sound detector for laughter and clapping.
\end{itemize}

\cvsection{Publication(s)}

\begin{itemize}
	\tightlist
	\item
	Md. Junaedur Rahman, Jesus Martinez Del-Rincon, Jean Christophe Nebel, Dimitrios Makris. Body pose based pedestrian tracking in a particle filtering framework. Submitted in MVA 2013, Kyoto, Japan.
\end{itemize}	

\cvsection{Leadership and Teamwork}

\begin{itemize}
\tightlist
\item
	Leaded a group of people to keep the flow of Microsoft products supply chain management in order.
\item
	Organized a workshop in Multimode Group, Microsoft Division.
\item
	Worked as a researcher in a team assisted on Software development and performance evaluation.
\item
	Worked for Ahsanullah University of Science and Technology Alumni Association.
\item
	Presided high school debating society and organized workshops to train present debaters who became champion on several television debating competitions.
\end{itemize}		